\chapter{Software Architecture Design}
\label{chap:software-architecture-design}

\section{System Architecture Overview}
\label{section:architecture-overview}
<TIP: Provide a high-level description of your system's structure.
Include either a Domain Model (to describe core business concepts
and their relationships)
or a Design Class Diagram (to describe how your code is organized
into classes and packages),
whichever best communicates your design.
Accompany your diagram with a short paragraph explaining the key
components and how they interact. />

\section{Software Design}
\label{section:software-design}
<TIP: Describe the runtime behavior of your system.
Include a Sequence Diagram for your most important use cases.
Focus on scenarios with non-trivial interactions between components.
If your project involves a novel algorithm,
describe it here and explain why you designed it this way. />

\section{AI and Data Design}
\label{section:ai-data-design}

\subsection{Data Sources and Collection}
<TIP: Describe where your data comes from. Is it collected from users,
scraped from the web, sourced from a public dataset, or
provided by an external API?
Explain how much data you have or plan to collect,
and any challenges you anticipate in obtaining it.
Explain how data is cleaned, transformed, or prepared before use. />
\subsection{Model Design}
<TIP: Describe the AI model or external AI service you plan to use.
Explain why you chose it over alternatives.
This can connect back to your competitor or literature review in Chapter 2.
If you are training your own model, describe the architecture and
training approach. If you are using a third-party model or API,
describe how it is integrated into your system and any prompt design
or fine-tuning involved. />
\subsection{Evaluation}
<TIP: Describe the metrics you plan to use to evaluate your AI model. />